Hierarchical Dispatching and Overriding

### 2017-10-10 NewVersion/sections/Formalization.tex
S3

\section{Formalization}~\label{sec:formalization}
In this section, we present the formal model called \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}), following similar style of 
Featherweight Java~\cite{Igarashi01FJ}. The syntax, typing rules,
small-step semantics and theorems for type soundness are presented.

@@

\paragraph{Methods}
The method declaration $\method{I}{m}{I_x}{x}{J}{e}$ introduces a
method named $m$ with result type $I$, parameters $\overline{x}$ of
type $\overline{I_x}$ and the overriding target $J$. The body of the
method is the single statement $ \kwreturn \; e;$. We also allow
defining abstract methods with $\absmethod{I}{m}{I_x}{x}{J}$, which is
similar to a normal method but without a method body. Notably, we have introduced the
\kwoverride{} keyword to override an old implementation of the
method. If the interface that it overrides is exactly the enclosing
interface, then such a method is seen as ``originally defined''; otherwise
it is hierarchical overriding.
For simplicity, overloading is not modelled for methods, which
implies that we can uniquely identify a method by its name.

@@

There are two typing rules for method invocation: \textsc{(T-Invk)}
and \textsc{(T-PathInvk)}. \textsc{(T-Invk)} is the typing judgement
for a normal method invocation. First it ensures that the method
receiver $e_0$ type checks to a type $I_0$. Then it checks the type of
the specific method, by using an auxiliary function $\mbody(m, I_0,
I_0)$, which is the function for looking up methods that we will
illustrate in more detail in Section~\ref{subsec:auxdefs}. The form of
\mbody{} is different to FJ, which has two parameters. The first $I_0$
represents the dynamic type and the second, the static type. If the
result of \mbody is not \Undefined, it means that the method exists and the corresponding method parameters and return types are given. After the method type is obtained, we check that all arguments $\overline{e}$ type check to $\overline{I}$ which are subtypes of $\overline{J}$. \textsc{(T-PathInvk)} is the typing judgement for a path invocation. Besides the conditions of \textsc{(T-Invk)}, \textsc{(T-PathInvk)} requires the type of receiver to be the subtype of the specified path type. 
% and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.

>>>>

\section{Formalization}~\label{sec:formalization}
In this section, we present the formal model called \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}), following similar style of 
Featherweight Java~\cite{Igarashi01FJ}. \MIM{} is a minimal core calculus that formalizes the core concept of hierarchical dispatch and overriding. The syntax, typing rules,
small-step semantics and theorems for type soundness are presented.

@@

\paragraph{Methods}
We allow the definition of two kinds of methods, ``original method'' and ``overriding method'', which share the same syntax. The method declaration $\method{I}{m}{I_x}{x}{J}{e}$ introduces a
method named $m$ with result type $I$, parameters $\overline{x}$ of
type $\overline{I_x}$ and the overriding target $J$. The body of the
method is the single statement $ \kwreturn \; e;$. Notably, we have introduced the
\kwoverride{} keyword to override an old implementation of the
method. If the interface that it overrides is exactly the enclosing
interface, then such a method is seen as ``originally defined'' and called ``original method''; otherwise it is an ``overriding method''. We also allow
defining abstract methods with $\absmethod{I}{m}{I_x}{x}{J}$, which is
similar to a normal method but without a method body. 
For simplicity, overloading is not modelled for methods, which
implies that we can uniquely identify a method by its name.

@@

\textsc{(T-Invk)} is the typing rule for method invocation.
 First it ensures that the method
receiver $e_0$ type checks to a type $I_0$. Then it checks the type of
the specific method, by using an auxiliary function $\mbody(m, I_0,
I_0)$, which is the function for looking up methods that we will
illustrate in more detail in Section~\ref{subsec:auxdefs}. The form of
\mbody{} is different to FJ, which has two parameters. The first $I_0$
represents the dynamic type and the second, the path type. The path type is the upcast type of $e_0$ (if any), else the path type is the same as its dynamic type. If the result of \mbody{} is not \Undefined, it means that the method exists and the corresponding method parameters and return types are given. After the method type is obtained, we check that all arguments $\overline{e}$ type check to $\overline{I}$ which are subtypes of $\overline{J}$. 
% \textsc{(T-PathInvk)} is the typing judgement for a path invocation. Besides the conditions of \textsc{(T-Invk)}, \textsc{(T-PathInvk)} requires the type of receiver to be the subtype of the specified path type. 
% and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.
